How fluid-mechanical erosion creates anisotropic porous media

### 2022-06-29 docs/PhysicsPaper/StokesErosion.tex
NM

Figure~\ref{fig5} shows the permeability and anisotropy measurements for the complete data set. In particular, for a given number of initial bodies ($M$ = 20, 40, 60, 80, or 100), the mean of each quantity (permeability or anisotropy) is shown with the vertical error bars representing the standard deviation. Different initial numbers of bodies, $M$, are shown by different colors. As seen in Figures~\ref{fig5}(a)--(b), the trends of increasing permeabilities are well grouped by the number of initial bodies. That is, permeability monotonically decreases with the number of bodies and the error bars shows little overlap between different values of $M$ until very late in the simulation when the bodies have nearly vanished.

Figure~\ref{fig5}(c) shows the corresponding statistics of anisotropy, $\anis$. Here, the anisotropy is not as well separated by $M$. That is, given the error-bars, there is significant overlap in the signal of $\anis$ across different values of $M$. One notable feature is a second rise in $\anis$ that occurs late in the simulation only for the larger values of $M$ = 60, 80, and 100. As before, the anisotropy can be decomposed into configuration and shape components as shown in Figures~\ref{fig5}(d)--(e). Here, we see the late surge in configurational anisotropy for these larger values of $M = $ 60, 80, 100. For these runs with a large number of bodies, the latest stages of erosion are dominated by channelization which substantially promotes the configurational anisotropy. The shape anisotropy, meanwhile, takes a more regular, parabolic form that is relatively insensitive to the number of bodies.

>>>>

Figure~\ref{fig5} shows the permeability and anisotropy measurements for the complete data set. In particular, for a given number of initial bodies ($M$ = 20, 40, 60, 80, or 100), the mean of each quantity (permeability or anisotropy) is shown with the vertical error bars representing the standard deviation. Different initial numbers of bodies, $M$, are shown by different colors. As seen in Figures~\ref{fig5}(a)--(b), the trends of increasing permeabilities are well grouped by the number of initial bodies. That is, permeability monotonically decreases with the number of bodies and the error bars shows little overlap between different values of $M$, until very late in the simulation when the bodies have nearly vanished.

	Figure~\ref{fig5}(c) shows the corresponding statistics of anisotropy, $\anis$. Notice that the anisotropy is not as well separated by $M$. That is, given the error-bars, there is significant overlap in the signal of $\anis$ across different values of $M$. For all values of $M$, the anisotropy initially increases and reaches a peak of roughly $\anis \approx 4$. Interestingly, for the runs featuring a large number of bodies $M = 60, 80, 100$, there is a second rise in anisotropy that occurs late in the simulation and results in a higher peak of roughly $\anis \approx 6$. Thus, the late surge of anisotropy, first observed in Fig.~\ref{fig3}, is not specific to that particular simulation. Rather, it occurs robustly across all simulations as long as the initial number of bodies is sufficiently large, $M \ge 60$.

 	As before, the anisotropy can be decomposed into configuration and shape components, and statistics of these quantities are shown in Figs.~\ref{fig5}(d)--(e). Most notably, the configurational anisotropy is seen to surge late in the erosion process in all of the simulations featuring a high body count, $M \ge 60$, suggesting the previously observed second rise in total anisotropy is due to the configurational component.

HERE

For these high-body count runs, the latest stages of erosion are dominated by channelization which substantially promotes the configurational anisotropy. The shape anisotropy, meanwhile, takes a more regular, parabolic form that is relatively insensitive to the number of bodies.
